---
title: "p8105_hw5_pc2853"
author: "pc2853"
date: "November 9, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
library(tidyverse)
library(rvest)
library(purrr)
library(ggplot2)
theme_set(theme_bw() + theme(legend.position = "bottom"))
```

###Problem 1

* Start with a dataframe containing all file names:

```{r p1 file name, message=FALSE}
p1_file_name = 
  tibble(
    path = str_c("./data/", list.files("data/"))[1:20],
    name = list.files("data/")[1:20]
  )

```

* Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe; 
* Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary:

```{r data cleaning, message=FALSE}

add_arm_id_and_read = function(x){
  read_csv(x) %>% 
    mutate(arm = str_sub(x, 8, 10), id = str_sub(x, 12, 13))
  
}

p1_data_tidy = 
  map_df(.x = p1_file_name$path, ~ add_arm_id_and_read(.x)) %>% 
  gather(key = week, value = weekly_observation, week_1:week_8) %>% 
  separate(week, into = c("remove", "week"), sep = "_") %>% 
  select(arm, id, everything(), -remove)
  
```

* Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups

```{r spaghetti plot, message=FALSE}
p1_data_tidy %>% 
  mutate(arm_id = paste(arm, id, sep = "_")) %>% 
  ggplot(aes(x = week, y = weekly_observation, color = arm, group = arm_id)) +
    geom_line() +
    labs(
      title = "Observations on each subject over time",
      x = "Week",
      y = "Weekly observation",
      color = 'Arm'
    ) 
```

Reading this plot, we know that the observations in experimental arm in generally larger than that in control arm, and only the experimental arm has increasing observations over time. 

###Problem 2

* Import the data:

```{r p2 data, message=FALSE}
p2_data = read_csv("./data/homicide-data.csv")
```

* describe the data:

The data has a dimension of `r dim(p2_data)`. It contains variables that are victims' id, reported date, victims' last name, victims' first name, their race, age, sex, city, state, latitude, longitude and disposition. 

* Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”):
```{r data mutation}
p2_data_mutated_total = 
  p2_data %>%
  mutate(city_state = paste(city, state, sep = ", ")) %>% 
  group_by(city_state) %>% 
  summarize(n_homicide_total = n())

p2_data_mutated_unsolved = 
  p2_data %>%
  ungroup() %>% 
  mutate(city_state = paste(city, state, sep = ", ")) %>% 
  filter(disposition == c("Closed without arrest", "Open/No arrest")) %>% 
  group_by(city_state) %>% 
  summarize(n_homicide_unsolved = n())

p2_data_mutate = 
  full_join(p2_data_mutated_total, p2_data_mutated_unsolved) %>% 
  filter(!is.na(n_homicide_unsolved) == TRUE)
```

* For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe:
```{r p2 part 2}
p2_data_Baltimore_MD =   
  p2_data_mutate %>% 
  filter(city_state == "Baltimore, MD")
prop.test(p2_data_Baltimore_MD$n_homicide_unsolved, p2_data_Baltimore_MD$n_homicide_total) %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high) %>% 
  knitr::kable(digits = 3)

```

